### 2010-09-08 BMD2010/PhysicalParameters/MooreHubbardSchwabKooijman_abstract.tex
got it on two pages

\section*{Introduction}
Accurate measurements of a bicycle's physical parameters are required for
realistic dynamic simulations and analysis. For the most basic models the
geometry, mass, mass location and mass distributions must be measured. More complex models
require measurements of tire characteristics, human characteristics, friction, stiffness, damping, etc. This
paper concerns the measurement of the minimal bicycle parameters required for
the benchmark bicycle presented in~\cite{Meijaard2007}. This
model is composed of four rigid bodies, has ideal rolling and frictionless joints,
and is assumed to be laterally symmetric. A set of 25
parameters is used to describe the geometry, mass, mass location and
mass distribution of each of the rigid bodies. These parameters are presented
relative to a reference frame when the bicycle is in the nominal upright
configuration. The experimental methods described herein are based primarily on the work
done in~\cite{Kooijman2006} but have been refined for improved accuracy and
methodology. Koojiman's was preceded by \cite{Roland1971} who measured an experimental bicycle frame in a
similar fashion and both~\cite{Dohring1953} and~\cite{Singh1971} who have used
similar techniques with scooters. We measured the characteristics of six
different bicycles, two of which were set up in two different configurations.
This is a total of eight different parameter sets that can be used with, but not
limited to, the benchmark bicycle model. The accuracy of all the measurements
are presented up through the eigenvalue prediction of the linear model and are
based error propogation theory with correlations taken into account.

@@

\section*{Experimental Methodology}
The benchmark bicycle requires five basic geometric measurements: wheelbase
$w$, steer axis tilt $\lambda$, trail $c$, and wheel radii $r_\mathrm{F}$
and $r_\mathrm{R}$. For each geometric measurement care was taken to measure
the parameter directly as possible with high accuracy measurement equipment
such as height gages, scales, etc. The mass of each of the rigid bodies were
measured with a precision scale. The centers of mass of each of the rigid
bodies were measured by hanging each rigid body at the mass center and
assuming lateral symmetry. The mass centers were calculated from the
orientation angle of the headtube and the location of the point of suspension
relative to the wheel center. The wheel centers of mass were assumed to be in
their ideal geometric center.

The moments of inertia of the rigid bodies were measured in both torsional
pendulum and compound pendulum configurations. Again the assumed symmetry of the
bicycle was utilized to reduce the number of measurements needed. The
in-symmetric-plane moments of inertia were calculated from measurements of the
rigid bodies' periods of oscillation when hung as a torsional pendulum at
different orientation angles. The out-of-plane moments of inertia were
measured by swinging the rigid bodies as a compound pendulum. The periods were
estimated from precision rate gyro measurements.
\section*{Results}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=3.5in]{../../report/figures/bike_eig.png}
    \end{center}
    \caption{Eigenvalues versus speed for all eight bicycle configurations.}
    \label{fig:bike_eig}
\end{figure}

Parameter sets with measurement uncertainties for all six bicycles and all
eight configurations  will be presented, together with basic comparisons of the
open loop dynamics of the different types of bicycles (eigenvalues,
eigenvectors, bode plots, etc). Notable results include high accuracy
measurements, dual oscillatory eigenmodes, bicycles without riders may often
have no stable speed range, and it is possible to calculate the uncertainties
in the eigenvalues and eigenvectors.

>>>>

\section*{Introduction}
Accurate measurements of a bicycle's physical parameters are required for
realistic dynamic simulations and analysis. For the most basic models the
geometry, mass, mass location and mass distributions must be measured. More complex models
require measurements of tire characteristics, human characteristics, friction, stiffness, damping, etc. This
paper concerns the measurement of the minimal bicycle parameters required for
the benchmark bicycle presented in~\cite{Meijaard2007}. This
model is composed of four rigid bodies, has ideal rolling and frictionless joints,
and is assumed to be laterally symmetric. A set of 25
parameters is used to describe the geometry, mass, mass location and
mass distribution of each of the rigid bodies. The experimental methods
described herein are based primarily on the work
done in~\cite{Kooijman2006} but have been refined for improved accuracy and
methodology. Koojiman's work was preceded by \cite{Roland1971} who measured a bicycle in a
similar fashion and both~\cite{Dohring1953} and~\cite{Singh1971} who have used
similar techniques with scooters. We measured the characteristics of six
different bicycles, two of which were set up in two different configurations.
This is a total of eight different parameter sets that can be used with, but not
limited to, the benchmark bicycle model. The accuracy of all the measurements
are presented up through the eigenvalue prediction of the linear model and are
based error propogation theory with correlations taken into account.

@@

\section*{Experimental Methodology}
The benchmark bicycle requires five basic geometric measurements: wheelbase
$w$, steer axis tilt $\lambda$, trail $c$, and wheel radii $r_\mathrm{F}$
and $r_\mathrm{R}$. For each geometric measurement care was taken to measure
the parameter directly as possible with high accuracy measurement equipment
such as height gages, scales, etc. The mass of each of the rigid bodies were
measured with a precision scale. The centers of mass of each of the rigid
bodies were measured by hanging each rigid body at the mass center under the
assumption of lateral symmetry. The mass centers were calculated from the
orientation angle of the headtube and the location of the point of suspension
relative to the wheel center. The wheel centers of mass were assumed to be
aligned with the geometric center.

The moments of inertia of the rigid bodies were measured in both torsional
pendulum and compound pendulum configurations. Again the assumed symmetry of the
bicycle was utilized to reduce the number of measurements needed. The
in-symmetric-plane moments of inertia were calculated from measurements of the
rigid bodies' periods of oscillation when hung as a torsional pendulum at
different orientation angles. The out-of-symmetric-plane moments of inertia were
measured by swinging the rigid bodies as a compound pendulum. The periods were
estimated from precision rate gyro measurements.
\section*{Results}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=3.25in]{../../report/figures/bike_eig.pdf}
    \end{center}
    \caption{Eigenvalues versus speed for all eight bicycle configurations.}
    \label{fig:bike_eig}
\end{figure}

Parameter sets with measurement uncertainties for all six bicycles and all
eight configurations  will be presented, together with basic comparisons of the
open loop dynamics of the different types of bicycles (eigenvalues,
eigenvectors, bode plots, etc), Fig.~\ref{fig:bike_eig}. Notable results include high accuracy
measurements, dual oscillatory eigenmodes, bicycles without riders may often
have no stable speed range, and it is possible to calculate the uncertainties
in the eigenvalues and eigenvectors.
